Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-19 paper/paper.tex
added source on table ii

We evaluated \tname\ against \Mar{@Lucas, please look for constant
  numbers as this *in text* and use macros instead. We do not want to
  leave inconsistent data in the paper!}14 attacks of various kinds, such as \Fix{...}\rui{add few examples}. The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top five rules in 
\percTopFiveRanking\ of the cases and ranked the correct rule among 
the top ten rules in \topTenAttacks of the \totalAttacks cases. \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

@@

      2100384 & - & ICMP Info & icmp & \textbf{icode}:0; \textbf{itype}:8; \\
      2100399 & - & ICMP Info & icmp & \textbf{icode}:1; \textbf{itype}:3; \\
      2100401 & - & ICMP Info & icmp & \textbf{icode}:0; \textbf{itype}:3; \\
      2100402 & - & ICMP Info & icmp & \textbf{icode}:3; \textbf{itype}:3; \\
      2100408 & - & ICMP Info & icmp & \textbf{icode}:0; \textbf{itype}:0; \\
      2100485 & - & ICMP Info & icmp & \textbf{icode}:13; \textbf{itype}:3; \\
      2100486 & - & ICMP Info & icmp & \textbf{icode}:10; \textbf{itype}:3; \\

>>>>

We evaluated \tname\ against \Mar{@Lucas, please look for constant
  numbers as this *in text* and use macros instead. We do not want to
  leave inconsistent data in the paper!}\totalAttacks attacks of various kinds, such as \Fix{...}\rui{add few examples}. The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top five rules in 
\percTopFiveRanking\ of the cases and ranked the correct rule among 
the top ten rules in \topTenAttacks of the \totalAttacks cases. \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

@@

      2100384 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:0; \textbf{itype}:8; \\
      2100399 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:1; \textbf{itype}:3; \\
      2100401 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:0; \textbf{itype}:3; \\
      2100402 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:3; \textbf{itype}:3; \\
      2100408 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:0; \textbf{itype}:0; \\
      2100485 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:13; \textbf{itype}:3; \\
      2100486 & \cite{iscx} & ICMP Info & icmp & \textbf{icode}:10; \textbf{itype}:3; \\
